### 2023-06-27 vesicle_code/docs/confinedMulti/multicomponent_vesicles.tex
yny at intro

%%%MAIN TEXT%%%%
\section{\label{sec:Introduction}Introduction}
Soft particles, such as vesicles, display rich dynamics when they are
subjected to different types of physical processes. These dynamics are
affected by parameters such as the capillary number, reduced volume, and
confinement ratio. Understanding these dynamics is critical to
understanding biophysical and microfluidic processes. For example, a
vesicle's reduced area and viscosity contrast will determine if it
undergoes tank treading, swinging, or tumbling in a shear
flow~\cite{nog-gom2005}. Transitions in the vesicle shape occur in
non-linear parabolic flows~\cite{kao-bir-mis2009, dan-vla-mis2009}, and
these shapes include axisymmetric bullets or parachutes, and asymmetric
parachutes. More recently, groups have considered these transitions when
vesicles are suspended in a channel or pipe
flow~\cite{lyu-che-far-jae-mis-leo2023, aga-bir2020, qua-gan-you2021,
abb-far-nai-ezz-ben-mis2022}. These dynamics include snaking and
swirling behaviors; croissant and slipper shapes; and semipermeability.

>>>>

%%%MAIN TEXT%%%%
\section{\label{sec:Introduction}Introduction}
Biological membranes have been observed to contain a vast array of proteins and different lipid species, that phase-separate and form domains resulting in spatial variations in material properties such as bending stiffness. Synthetic multicomponent vesicles, self-enclosed lipid bilayer membranes composed of different lipid species, have been used to study the rich patterns and accompanying morphologies which emerge from elastic heterogeneity in the membrane.

Soft particles, such as vesicles, display rich dynamics when they are
subjected to different types of physical processes. These dynamics are
affected by parameters such as the capillary number, reduced volume, and
confinement ratio. Understanding these dynamics is critical to
understanding biophysical and microfluidic processes. For example, a
vesicle's reduced area and viscosity contrast will determine if it
undergoes tank treading, swinging, or tumbling in a shear
flow~\cite{nog-gom2005}. Transitions in the vesicle shape occur in
non-linear parabolic flows~\cite{kao-bir-mis2009, dan-vla-mis2009}, and
these shapes include axisymmetric bullets or parachutes, and asymmetric
parachutes. More recently, groups have considered these transitions when
vesicles are suspended in a channel or pipe
flow~\cite{lyu-che-far-jae-mis-leo2023, aga-bir2020, qua-gan-you2021,
abb-far-nai-ezz-ben-mis2022}. These dynamics include snaking and
swirling behaviors; croissant and slipper shapes; and semipermeability.
